---
title: "Advertising Analysis"
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
  html_notebook: default
---


Lets load our data from python & begin our analysis. 
```{r}
library(readr)
library(ggplot2)
library(gvlma)

  #set a seed to be reproducable 
set.seed(13)
data <- read.table("data.csv", header = TRUE, sep = ",")
data <- as.data.frame(data)

  #rename 'i..Date' to 'Date'
names(data)[1] <- c("Date")

  #set data types

data$Sales <- as.numeric(data$Sales)
data$Date <- as.Date(data$Date, "%m/%d/%Y")
data$Image <- as.factor(data$Image)
data$Post <- as.factor(data$Post)

  #create a set of only 2019+ data
data_PY = data[data$Date >= '2019-01-01',]

head(data)
head(data_PY)
```




Check for outliers in Sales
```{r}
boxplot(data_PY$Sales)


data_PY = data_PY[data_PY$Sales < 20000,]

boxplot(data_PY$Sales)
summary(data_PY$Sales)

hist(data_PY$Sales)

```

Lets start with a standard linear model, testing if the required assumptions for OLS hold. 
```{r}
library(MASS)

model1 <- lm(data = data_PY, Sales ~ Post)
summary(model1)
plot(model1)
gvlma(model1)
```

Unfornuately for us, we can see the first model doesn't satisfy our assumptions. Using it would result in potentially unreliable and innacurate findings. 

Now lets try a log-lin model, performing a logarithming transformation on the Sales variable.

```{r}
data_PY$z<-  (data_PY$Sales-min(data_PY$Sales))/(max(data_PY$Sales)-min(data_PY$Sales))
model2 <- lm(data=data_PY, (Sales**(1/8)) ~ Post)
summary(model2)
plot(model2)
gvlma(model2)
```
Great, looks like we have a winner. We can see our assumptions are met. Now for the slighly tricky bit. This model can be interepreted as "a X% change in Sales results from a Post". 

Based on the coefficients, we can see that a day with a post, on average, increases sales by 15.8%. 

Let's perform a differnt form of statistical test to verify our findings. We can use a simple T-test to see if the means statistically differ between days with a Facebook post, and days without. 




T-Test to confirm difference
```{r}
t_test <- t.test(data_PY$Sales[data_PY$Post == 1],data_PY$Sales[data_PY$Post == 0] )
t_test
summary(t_test)

ggplot(data = data_PY, aes(Post, Sales, color = Post)) + geom_boxplot() + geom_jitter() 


mean(data_PY$Sales[data_PY$Post == 0])

ggplot(data = data.frame(post=as.factor(c('No Post','Post')), m=c(mean_sales_no_post, mean_sales_with_post))
       ,aes(x=post, y=m)) + geom_bar(stat='identity', fill='dodgerblue3')
```

We can see that our t-statistic is 2.707, meaning if we believed there was no statistical difference between the two means (that they both were equal), we'd expect to see this type of result .8% of the time. We can safely conclude that there is a statistically significant differnce between days with posts and days without. 

In addition, we can construct a confidence interval for our hypothesis. Per the output, we can be 95% certain that the true difference a Facebook post makes is between $85.71 and $559.43. Yes.... sadly this is a large range, but luckily for us this is significantly different from zero, meaning our posts do make an impact. 



```{r}
mean_sales_with_post <- mean(data_PY$Sales[data_PY$Post == 1])
mean_sales_no_post <- mean(data_PY$Sales[data_PY$Post == 0])

mean_sales_no_post * .158

hist(data_PY$Sales)
hist(log10(data_PY$Sales))
```






How many days in the last year did we not advertise?

```{r}
length(data_PY$Sales[data_PY$Post == 0])

ggplot(data = data.frame(post=as.factor(c('No Post','Post')), m=c(280, 54))
       ,aes(x=post, y=m)) + geom_bar(stat='identity', fill='dodgerblue3')
```


What is our estimated lost revenue, with a 95% confidence interval. 

Let's see if we advertised an additional 1 out of ever 3 days, and anticipating that only 75% of our posts are effectve in generating additional customers. 

```{r}

  #construct a 95% confidence interval around Post1 coefficient
conf_interval = confint(model2, "Post1", .95)



missed_revenue <- function(pct_addlt_adv, pct_effective){
  
  min = pct_addlt_adv * pct_effective * 280 * mean_sales_no_post * conf_interval[1]
  mean = pct_addlt_adv * pct_effective  * 280 * mean_sales_no_post * .158
  max = pct_addlt_adv * pct_effective  * 280 * mean_sales_no_post * conf_interval[2]
  
  print(paste(pct_addlt_adv * 280, "additional days of advertising"))
  sprintf("$%.2f -- $%.2f -- $%.2f",min, mean, max)

}

#Missed_revenue(% of additional days advertised, % of advertisements that were effective)

missed_revenue(.33, .5)
```

